---
title: "vismi-vignettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vismi-vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  tidy.opts = list(width.cutoff = 60), tidy = TRUE,
  dpi = 200, fig.asp = 0.5, fig.width = 7, fig.retina = 1,
  out.width = "95%",
  warning = FALSE, message = FALSE
)
```

```{r setup}
#devtools::document()
#devtools::load_all()
library(mixgb)
library(vismi)

```

#Overimputation

```{r}
data(nhanes3_newborn)
set.seed(2023)

n=nrow(nhanes3_newborn)
idx=sample(1:n, size = round(0.7*n), replace=FALSE)

trainNA.df=nhanes3_newborn[idx,]
testNA.df=nhanes3_newborn[-idx,]

```


##Overimputation with the entire dataset
Note that overimputation with training and test set can only be used with "mixgb" and "miae" method.
```{r}
#overimpute the whole dataset using mixgb
mixgb.obj<-overimpute(train.data=nhanes3_newborn,p=0.3,m=2, method = "mixgb")
```

Methods within "mice" can only use overimputation with the entire dataset.

```{r}
#overimpute the whole dataset using mice default
mice.obj<-overimpute(train.data=nhanes3_newborn,p=0.3,m=5, method = "mice")
```

```{r,eval=FALSE}
#overimpute the whole dataset using mice cart
cart.obj<-overimpute(train.data=nhanes3_newborn,p=0.3,m=5, method = "cart")
```
```{r,eval=FALSE}
#overimpute the whole dataset using mice ranger
rf.obj<-overimpute(train.data=nhanes3_newborn,p=0.3,m=5, method = "rf")
```


## trelliscope: plot all continuous variables
```{r}
trelliscope_con(obj=mice.obj,train.data=nhanes3_newborn,type="ridge")
```

```{r}
trelliscope_con(obj=mice.obj,train.data=nhanes3_newborn,type="density")
```
```{r}
trelliscope_con(obj=mice.obj,train.data=nhanes3_newborn,type="qq")
```

## trelliscope: plot all categorical variables

```{r}
trelliscope_cat(obj=mice.obj,train.data=nhanes3_newborn, type = "identity")
```

```{r}
trelliscope_cat(obj=mice.obj,train.data=nhanes3_newborn, type = "dodge")
```


##Overimputation with the training set and test set


```{r}
train_test.obj<-overimpute(train.data=trainNA.df,test.data=testNA.df,p=0.3, m=5, method = "mixgb")
```


## trelliscope: all continuous variables
```{r}
trelliscope_con(obj=train_test.obj,train.data=trainNA.df,test.data=testNA.df,type="ridge")
```


```{r}
trelliscope_con(obj=train_test.obj,train.data=trainNA.df,test.data=testNA.df, type="density")
```

```{r}
trelliscope_con(obj=train_test.obj,train.data=trainNA.df,test.data=testNA.df, type = "qq")
```

## trelliscope: all categorical variables
```{r}
trelliscope_cat(obj=train_test.obj,train.data=trainNA.df,test.data=testNA.df, type = "identity")
```
## trelliscope: all categorical variables
```{r}
trelliscope_cat(obj=train_test.obj,train.data=trainNA.df,test.data=testNA.df, type = "dodge")
```



## Plot an individual variable: some randomly selected entries of overimputed values 
### Actual
```{r,fig.asp = 1}
plot1D.entries(obj=train_test.obj,var.name="BMPHEAD", train.data=trainNA.df,test.data=testNA.df)
plot1D.entries(obj=train_test.obj,var.name="HYD1", train.data=trainNA.df,test.data=testNA.df,n.entries=10)
```

## Plot an individual variable: some randomly selected entries of overimputed values 
### Error
```{r}
plot1D.entriesV2(obj=train_test.obj,var.name="BMPHEAD", train.data=trainNA.df,test.data=testNA.df,n.entries=10)


plot1D.entriesV2(obj=train_test.obj,var.name="HYD1", train.data=trainNA.df,test.data=testNA.df,n.entries=10)
```

## Plot an individual variable:  m sets of overimputed values vs true values
```{r}
plot1D.imputations(obj=train_test.obj,var.name="BMPHEAD", train.data=trainNA.df,test.data=testNA.df)
plot1D.imputations(obj=train_test.obj,var.name="HYD1", train.data=trainNA.df,test.data=testNA.df)
```
## Plot an individual variable:  overlaying density
```{r}
plot1D.imputationsV2(obj=train_test.obj,var.name="BMPHEAD", train.data=trainNA.df,test.data=testNA.df)

plot1D.imputationsV3(obj=train_test.obj,var.name="BMPHEAD", train.data=trainNA.df,test.data=testNA.df)

#plot1D.imputations(obj=train_test.obj,var.name="BMPHEAD", train.data=trainNA.df,test.data=testNA.df, type = "qq")



plot1D.imputationsV4(obj=train_test.obj,var.name="BMPHEAD", train.data=trainNA.df,test.data=testNA.df)


plot1D.imputationsV2(obj=train_test.obj,var.name="HYD1", train.data=trainNA.df,test.data=testNA.df)
#plot1D.imputations(obj=train_test.obj,var.name="HYD1", train.data=trainNA.df,test.data=testNA.df, type = "dodge")
```


## Plot tow variables:  m sets of overimputed values vs true values
```{r,fig.width = 5,fig.height=8,fig.asp = 1.2}
plot2D(obj=train_test.obj,var.x="BMPHEAD", var.y="BMPRECUM",train.data=trainNA.df,test.data=testNA.df)
```


## Overimputation with an entire dataset
When overimputing with an entire dataset, we can also use the above plotting functions without providing the `test.data`.
### plot an individual variable
```{r,fig.width = 5,fig.asp = 1, out.width = "50%",fig.retina = 1,dpi=200}
plot1D.entries(obj=mice.obj,var.name="BMPHEAD", train.data=nhanes3_newborn)
```
