---
title: "Visualisation for Convergence Diagnostics"
format:
  html:
    toc: true
    page-layout: full
    fig-format: svg
---

```{r,include=FALSE}
#| label: setup
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  dpi = 100,
  fig.retina = 1,
  fig.width = 9,
  fig.height = 5,
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```

## Obtain imputation objects from mice and mixgb

For demonstration, we use the `newborn` dataset included in the **vismi** package. This is an incomplete dataset with missing values in variables of various types.

We first obtain imputation objects from both the **mice** and **mixgb** packages with 5 multiple imputations (`m = 5`) and 10 iterations (`maxit = 10`).

```{r}
library(vismi)
library(mice)
library(mixgb)


set.seed(2026)
mice_obj <- mice(data = newborn, m = 5, maxit = 30, printFlag = FALSE)
mixgb_obj <- mixgb(data = newborn, m = 5, maxit = 30, save.models = TRUE)
mixgb_pmm_obj <- mixgb(data = newborn, m = 5, maxit = 30, pmm.type = "auto", save.models = TRUE)
```

### Visualise convergence diagnostic for mice object

```{r}
vismi_converge(obj = mice_obj, x = "recumbent_length_cm", tick_vals = NULL, linewidth = 0.5, mean_lim = c(68, 70.5), sd_lim = c(3, 8))
```

### Visualise convergence diagnostic for mixgb object (with PMM)

```{r}
vismi_converge(obj = mixgb_pmm_obj, x = "recumbent_length_cm", tick_vals = NULL, linewidth = 0.5, mean_lim = c(68, 70.5), sd_lim = c(3, 8))
```

### Visualise convergence diagnostic for mixgb object (without PMM)

```{r}
vismi_converge(obj = mixgb_obj, x = "recumbent_length_cm", tick_vals = NULL, linewidth = 0.5, mean_lim = c(68, 70.5), sd_lim = c(3, 8))
```

::: callout-note
## Convergence diagnostic for mixgb object

To use `vismi_converge()` for **mixgb** object, users are required to set `save.models = TRUE` in `mixgb()` so that intermediate summary statistics for imputations would be saved at each iteration for plotting convergence diagnostics.
:::
