---
title: "Inspecting distributional characteristics"
format:
  html:
    toc: true
    page-layout: full
    fig-format: svg
---

## Introduction 
```{r,include=FALSE}
#| label: setup
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  dpi = 100,
  fig.retina = 1,
  fig.width = 9,
  fig.height = 3.5,
  out.width = "100%"
)
```


```{r}
#| fig-show: hide
library(vismi)
vismi(data = newborn, imp_list = imp_newborn, x = "head_circumference_cm", verbose = TRUE)
```

## 1D visualsation

### 1 numeric variable
#### Static
```{r}
vismi(data = newborn, imp_list = imp_newborn, x = "head_circumference_cm", 
      marginal_x = "box+rug")
```

#### Interactive
```{r, out.height="550px"}
vismi(data = newborn, imp_list = imp_newborn, x = "head_circumference_cm", interactive = TRUE, marginal_x = "box+rug")
```

### 1 factor variable
#### Static
```{r}
vismi(data = newborn, imp_list = imp_newborn, x = "smoke")
```
#### Interactive
```{r, out.height="550px"}
vismi(data = newborn, imp_list = imp_newborn, x = "smoke", interactive = TRUE)
```



## 2D visualisation
### 2 numeric variables
#### Static 
```{r}
vismi(data = newborn, imp_list = imp_newborn, x = "head_circumference_cm", y = "recumbent_length_cm", 
      marginal_x = "box+rug",  marginal_y = "box+rug")
```

#### Interactive
```{r, out.height="550px"}
vismi(data = newborn, imp_list = imp_newborn, x = "head_circumference_cm", y = "recumbent_length_cm", interactive = TRUE, marginal_x = "box+rug", marginal_y = "box+rug")
```



### 1 factor 1 numeric variable 
#### Static 
```{r}
#| fig-width: 9
#| fig-height: 4
vismi(data = newborn, imp_list = imp_newborn, x = "recumbent_length_cm", y = "sex")
```

#### Interactive
```{r, out.height="550px"}
vismi(data = newborn, imp_list = imp_newborn, x = "recumbent_length_cm", y = "sex", interactive = TRUE)
```



### 2 factor variables 
#### Static 
```{r}
#| fig-width: 9
#| fig-height: 5
vismi(data = newborn, imp_list = imp_newborn, x = "sex", y = "smoke")
```

#### Interactive
```{r, out.height="550px"}
vismi(data = newborn, imp_list = imp_newborn, x = "sex", y = "smoke", interactive = TRUE)
```



## 3D visualisation
### 3 numeric variables 
#### Static 
```{r}
#| fig-width: 9
#| fig-height: 5
vismi(data = newborn, imp_list = imp_newborn, x = "recumbent_length_cm", y = "head_circumference_cm", z = "weight_kg")
```

#### Interactive
```{r, out.height="550px"}
vismi(data = newborn, imp_list = imp_newborn, x = "recumbent_length_cm", y = "head_circumference_cm", z = "weight_kg", interactive = TRUE, point_size = 3)
```

### 1 factor 2 numeric variables
#### Static 
```{r}
#| fig-width: 9
#| fig-height: 5
vismi(data=newborn,imp_list=imp_newborn,x="head_circumference_cm",y="smoke", z="recumbent_length_cm")
```

#### Interactive
```{r, out.height="550px"}
vismi(data = newborn, imp_list = imp_newborn, x="head_circumference_cm",y="smoke", z="recumbent_length_cm", interactive = TRUE, point_size = 3)
```


### 2 factor 1 numeric variables
#### Static 
```{r}
#| fig-width: 9
#| fig-height: 5
vismi(data=newborn,imp_list=imp_newborn,x="head_circumference_cm",y="sex",z="smoke")
```

#### Interactive
```{r, out.height="550px"}
vismi(data=newborn,imp_list=imp_newborn,x="head_circumference_cm",y="sex",z="smoke", interactive = TRUE, point_size = 3)
```


### 3 factor variables
#### Static 
```{r}
#| fig-width: 9
#| fig-height: 6
vismi(data=newborn,imp_list=imp_newborn,x="sex", y="race", z="smoke")
```

#### Interactive
```{r, out.height="550px"}
vismi(data=newborn,imp_list=imp_newborn,x="sex", y="race", z="smoke",interactive = TRUE)
```
